Title here

### 2016-12-12 portfolio/text/ms.Rmd
Edit results + methods

- concerning because in many areas of the world and fisheries, regulations and
  market forces have encouraged specialization
- permit diversity result: a privileged position --- expensive to get into
- locking into permits limits ability to pick lower risk strategies and is
  getting people locked into low diversity permits that may be doing well now,
  but not necessarily always

@@

@@

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.

@@

\noindent Again, $S_{i,t}$ and $I_{i,t}$ represent, respectively, percent change
in species diversity and an indicator variable for increasing or decreasing
species diversity. We exponentiate the equation to ensure all scale parameters,
$\sigma_{i,t}$, are positive. The $\gamma$'s are estimated coefficients, three
of which are allowed to vary by strategy, constrained by normal distributions:

@@

We fit our models with Stan 2.11.1 [@hoffman2014; @standevelopmentteam2015;
@standevelopmentteam2015a; @carpenter2015] and R 3.3.1 [@rcoreteam2016]. Stan
implements the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm
[@hoffman2014] to perform Bayesian statistical inference. We assigned weakly
informative priors on all parameters: $N(0, 2^2)$ priors on all $\beta$,
$\gamma$, and $\eta$ parameters, and half-$t(3, 0, 2)$ priors (i.e. degrees of
freedom of 3 and scale of 2) on all $\sigma$ and $\tau$. We ran four chains and
2,000 iterations and discarded the first 1,000 iterations of each chain as warm
up. We checked for chain convergence visually with trace plots, ensured that
$\hat{R}<1.05$ (the potential scale reduction factor) and that the effective
sample size, as calculated by the rstan R package [@standevelopmentteam2015],
was greater than 200 for all parameters [@gelman2014]. We verified that our
model returned sensible estimates by comparing our estimates to an ad-hoc
two-stage model fit with the lme4 R package [@bates2015], where we first fit
a mixed-effect regression model to the mean, and then modelled the absolute
residuals from that first model in a second mixed effects model representing the
variance component. We also validated the model with simulated data, and were
able to recover the true values (Supporting Information). Code used in our
analysis is available at <https://github.com/NCEAS/pfx-commercial/portfolios/>.

*TODO: move the following into the results section or into the methods section:*

Residuals from the mean component of our model clearly show the "V"-shaped
pattern that the variance component of our model seeks to capture (Fig.
S\ref{fig:resid}). Furthermore, the downside residuals (year-individual data
points with lower than expected revenue) look qualitatively similar to the
complete set of residuals (upside and downside) (Fig.
S\ref{fig:resid-downside}). Therefore, it seemed appropriate to model the
variability as a proxy for revenue risk.

The estimated year-permit intercepts represent years when people with
a particular permit set in a given year tended to do better or worse than the
long-term average for that permit set (Fig. S\ref{fig:str-yrs}). Therefore, an
individual's expected revenue and variability is after accounting for the
general trend in revenue for that permit set.

Our model estimates overall average effects (Fig. S\ref{fig:fe}) and effects
that vary by permit set (Fig. S\ref{fig:re}).

>>>>

- concerning because in many areas of the world and fisheries, regulations and
  market forces have encouraged specialization / limited (effective)
  diversification (e.g. multiple permits or diverse permits)
- locking into permits limits ability to pick lower risk strategies and is
  getting people locked into low diversity permits that may be doing well now,
  but not necessarily always

@@

<!-- TODO: get fig:re in results -->
<!-- Our model estimates overall average effects (Fig. S\ref{fig:fe}) and effects -->
<!-- that vary by permit set (Fig. S\ref{fig:re}). -->

@@

\noindent This approach, combined with the lack of a global intercept,
constrains the mean change in log revenue across all fishers and years to be
zero. I.e., we assume that the data are stationary after accounting for all
covariates and including an intercept that varies with strategy-year
combinations. Initial versions of the model confirmed that the global intercept
along with strategy-level intercepts would be estimated at almost exactly zero.
The estimated $\beta_{j,t}$'s represent years when people with a particular
permit set tended to do better or worse than the long-term average for that
permit set (Fig. S\ref{fig:str-yrs}). Therefore, an individual's expected
revenue (and variability) is after accounting for the general trend in revenue
for that permit set.

@@

\noindent Again, $S_{i,t}$ and $I_{i,t}$ represent, respectively, percent change
in species diversity and an indicator variable for increasing or decreasing
species diversity. We exponentiate the equation to ensure all scale parameters,
$\sigma_{i,t}$, are positive. Residuals from the mean component of our model
clearly show a "V"-shaped pattern that the variance component of our model can
capture (Fig. S\ref{fig:resid}). Furthermore, the downside residuals
(year-individual data points with lower than expected revenue) look
qualitatively similar to the complete set of residuals (upside and downside)
(Fig. S\ref{fig:resid-downside}). Therefore, it seemed appropriate to model the
variability as a proxy for revenue risk.

The $\gamma$'s are estimated coefficients, three of which are allowed to vary by
strategy, constrained by normal distributions:

@@

We fit our models with Stan 2.11.1 [@hoffman2014; @standevelopmentteam2015;
@standevelopmentteam2015a; @carpenter2015] and R 3.3.1 [@rcoreteam2016]. Stan
implements the No-U-Turn Hamiltonian Markov chain Monte Carlo algorithm
[@hoffman2014] to perform Bayesian statistical inference. We assigned weakly
informative priors on all parameters: $N(0, 2^2)$ priors on all $\beta$,
$\gamma$, and $\eta$ parameters, and half-$t(3, 0, 2)$ priors (i.e. degrees of
freedom of 3 and scale of 2) on all $\sigma$ and $\tau$. We ran four chains and
2,000 iterations and discarded the first 1,000 iterations of each chain as warm
up. We checked for chain convergence visually with trace plots, ensured that
$\hat{R}<1.05$ (the potential scale reduction factor) and that the effective
sample size, as calculated by the rstan R package [@standevelopmentteam2015],
was greater than 200 for all parameters [@gelman2014]. We verified that our
model returned sensible estimates by comparing our estimates to an ad-hoc
two-stage model fit with the lme4 R package [@bates2015], where we first fit
a mixed-effects regression model to the mean, and then modelled the absolute
residuals from that first model in a second mixed-effects model representing the
variance component. We also validated the model with simulated data, and were
able to recover the true values (Supporting Information). Code used in our
analysis is available at <https://github.com/NCEAS/pfx-commercial/portfolios/>.
